---
title: "Lab 4"
author: "Drew Hoffman, Tanner Ball, Burke Parent, David Washburn, Brandon Nelsen"
date: "9/20/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include = FALSE}
library(tidyverse)
babies <- read_csv("https://raw.githubusercontent.com/ervance1/Sp2018-Data-Science-repo/master/babies2a.dat")
babies <- rename(babies, bwtoz = 'bwt/oz') #renaming `bwt/oz` because the "/" sign requires special care
options(warn = -1)
```

**Tanner Individual Graph**
```{r}
ggplot(data=babies, mapping=aes(x=number, y=bwtoz))+geom_jitter()+facet_wrap(~ Premature)
```

**Drew Individual Graph**

```{r}
ggplot(data = babies, mapping = aes(x = gestation, y = bwtoz)) + geom_smooth(se = FALSE) + facet_wrap(~smoke)
```

**Brandon Individual Graph**
```{r}
babies$Premature <- as.numeric(babies$Premature)
babies$Premature <- as.factor(babies$Premature)
ggplot(data = babies)+
  geom_point(mapping = aes(x = babies$mpregwt, y = babies$bwtoz, color = babies$Premature))+
  theme(legend.position = "bottom")+
  guides(color = guide_legend(nrow = 1, override.aes = list(size = 2)))+
  geom_smooth(mapping = aes(x = babies$mpregwt, y = babies$bwtoz), se = FALSE, method = 'lm', color = "black")
```

**Burke's Individual Plot**
```{r, echo=FALSE}
ggplot(data = babies, mapping=aes(x = bwtoz, y = gestation))+
  geom_jitter()+facet_wrap(~smoke)+
  labs(title = "Relationship Between Gestation and Birth Weight For Smokers/Non-Smokers",subtitle= "0 = Never Smokes, 1 = Always Smokes", x = "Gestation Period, Days", y = "Birth Weight, Ounces")

```


*My question is fairly straightforward: Is there a difference between birth weight and gestation period for smokers and non-smokers? I decided to look at this graphically, and it seems to me that the largest noticeable difference of these two graphs is that the nonsmoker's data looks like it has a lot tighter spread while the smoker's spread is much wider. Also, birth weight looks similar between the two graphs while the gestation is more varied for the smoker group.*


**Team Report**
I, Burke Parent, decided to use non-default functions that include "Facet_wrap", so I can easily see the difference between smokers and non-smokers. I also created a title, substitle, and axis titles so the it is easier to understand what the graph is representing. I also used "geom_jitter" just in case any data points overlapped eachother. I also contributed to the team effort of the Lab Report by helping to come up with our two overall questions we set out to answer. I also helped in making one of the plots to help answer the one of the overall questions.