---
title: "Lab 4"
author: "Drew Hoffman, Tanner Ball, Burke Parent, David Washburn, Brandon Nelsen"
date: "9/20/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include = FALSE}
library(tidyverse)
babies <- read_csv("https://raw.githubusercontent.com/ervance1/Sp2018-Data-Science-repo/master/babies2a.dat")
babies <- rename(babies, bwtoz = 'bwt/oz') #renaming `bwt/oz` because the "/" sign requires special care
options(warn = -1)
```

**1. Overall Questions:**

**2. Team Plots:**


**3. Recommendation:**


**4. Preliminary Question:**


**5. Individual Graphs:**

**Tanner Individual Graph**
```{r}
ggplot(data=babies, mapping=aes(x=number, y=bwtoz))+geom_jitter()+facet_wrap(~ Premature)
```

**Drew Individual Graph**

The data shown depicts the relationship between gestation period in days and the weight at birth in ounces. It is then divided between smokers and non-smokers. As you can see from the slope of the regression lines, low birthweight for smoking mothers has a much more pronounced effect on premature babies, those who have spent less than 270 days in the womb. The distribution of points is lower for the smokers section.

```{r}
ggplot(data = babies, mapping = aes(x = gestation, y = bwtoz)) + geom_point() + geom_smooth(se = FALSE) + facet_wrap(~smoke) 
```

**Brandon Individual Graph**
```{r}
babies$Premature <- as.numeric(babies$Premature)
babies$Premature <- as.factor(babies$Premature)
ggplot(data = babies)+
  geom_point(mapping = aes(x = babies$mpregwt, y = babies$bwtoz, color = babies$Premature))+
  theme(legend.position = "bottom")+
  guides(color = guide_legend(nrow = 1, override.aes = list(size = 2)))+
  geom_smooth(mapping = aes(x = babies$mpregwt, y = babies$bwtoz), se = FALSE, method = 'lm', color = "black")
```

**David Individual Graph**
These data show the relationship between gestation and birth weight. The data suggest a positive relation between the two, indicated by the green line. The data is centered around 270 days, which is when a baby is expected to be born. Also, the plot shows the number of cigarretes smoked among mothers, with lighter shades indicating a greater number of cigarretes smoked. 
```{r}
ggplot2::babies
ggplot(data = babies, aes(x = gestation, y = bwtoz, color = number)) +
  geom_point() +
  geom_smooth(method = lm, color = "green")
```

**6. Who Did What:**